Posterior comparison methods

### 2022-11-04 src/explore_posterior-comparison/posterior-comparison.Rmd
Add SBC intuition and example in Stan code

ks_results %>%
  group_by(type) %>%
  summarise(mean = mean(D)) %>%
  kable()
```

@@

@@

>>>>

ks_results %>%
  group_by(type) %>%
  summarise(mean = mean(D)) %>%
  knitr::kable()
```

@@

## Intuition

There are two procedures you could use to generate samples from the joint distribution.
Firstly, you could sample from the prior on $\theta$ first:
$$
\tilde \theta_1 \sim p(\theta) \\
\tilde y_1 \sim p(y \, | \, \tilde \theta_1) \\
\implies (\tilde \theta_1, \tilde y_1) \sim p(\theta, y)
$$
Secondly, you could sample from the "prior" on $y$ first:
$$
\tilde y_2 \sim p(y) \\
\tilde \theta_2 \sim p(\theta \, | \, \tilde y_2) \\
\implies (\tilde \theta_2, \tilde y_2) \sim p(\theta, y)
$$
Both will generate samples from the joint distribution $p(\theta, y)$.
This implies that if you look at the draws from procedure one $\{ \tilde \theta_1\}$ and the draws from procedure two $\{ \tilde \theta_2\}$ then they have the same distribution.

Importantly, **procedure two involves computing a posterior distribution**, and therefore the samples will only be the same if the Bayesian inference procedure is exact.
It's this fact which SBC uses to create a procedure for checking implementation and accuracy of a given approximate Bayesian inference method.

@@

## Example from Stan manual

Consider the model:

$$
y_i \sim \mathcal{N}(\mu, \sigma^2) \\
\mu \sim \mathcal{N}(0 , 1) \\
\sigma \sim \text{lognormal}(0, 1)
$$

Want `M` samples.

```{r}
M <- 1000

n_chains <- 4
n_iter <- 2000

fit <- rstan::stan(file = "sbc.stan", iter = n_iter, chains = n_chains, refresh = 0)
```

Check that all ESS are greater than `M`:

```{r}
all(summary(fit)$summary[, "n_eff"] > M)
```

Extract samples and thin down to just `M`:

```{r}
samples <- extract(fit)
samples <- lapply(samples, function(sample) sample[1:M * floor(length(sample) / M)])
```

So, the quantiles (you probably want to be more careful about ranks than I'm being here) of the simulated data within the posterior are:

```{r}
sum(samples$mu_lt_sim) / length(samples$mu_lt_sim)
sum(samples$sigma_lt_sim) / length(samples$sigma_lt_sim)
```

These should be $\mathcal{U}(0, 1)$, so by repeating this process many times (it looks like it's a quite costly procedure!) we can assess whether this is in fact true.
